Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 egpaper_final.tex
3.4 (FFT part) collapsed into 3.2
minor change

We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both more discriminative than WHO, and can be generated in 70ms (compared to several seconds for WHO). This speed up means we can generate templates on the fly, allowing our approach to evaluate arbitrary viewpoint hypotheses.

@@

\begin{table*}[!htbp]
    \begin{center}
\begin{tabular}{|c|c|r|c|r|}
\hline
Methods (AP/MPPE) & before calibration  & time & after Calibration \cite{Aubry14} & time \\
\hline\hline
HOG\cite{Dalal05}     & 72.3 / 65.0  &  31ms  & 60.4 / 50.2                 &   8.7 sec \\ 
WHO\cite{Hariharan12} & 82.1 / 85.4  &  3811ms&                             &   12.4 sec  \\
WHO-CG                & 81.7 / \textbf{84.9}  &  104ms &     83.7 / 87.3             &   8.3 sec \\
WHO-CG-Z              & 54.4 / 65.1  &  103ms & \textbf{92.8} / 86.7 &   8.7 sec  \\
% NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
NZ-WHO-CG        & \textbf{90.0} / 82.8 & 79ms & 90.3 / \textbf{86.8}                   &  8.5 sec   \\
\hline
\end{tabular}
\end{center}
\caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11} variations of WHO on 3DObject Car dataset\cite{Savarese07}. WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO. WHO-CG-Z uses whiten the whole template and zero out textureless region. NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method. The time column indicates the time to generate one template. We followed calibration procedure presented in \cite{Aubry14}.}
\label{tab:who_initializations}
\end{table*}

>>>>

We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), that are both more discriminative than WHO, and can be generated in 70ms (compared to several seconds for WHO). This speed up means we can generate templates on the fly, allowing our approach to evaluate arbitrary viewpoint hypotheses. 
\scream{chris:We propose Non-Zero Whitened Histograms of Orientations (NZ-WHO), an improvement over WHO which is both more discriminative than WHO and can be computed many orders of magnitude faster than WHO (70ms as opposed to to several seconds for WHO). This speedup allows us to generate NZ-WHO templates on the fly, allowing us to quickly evaluate arbitrary viewpoint hypotheses.}

@@

\begin{table*}[!htbp]
    \begin{center}
\begin{tabular}{|c|c|r|c|r|}
\hline
Methods (AP/MPPE) & before calibration  & time & after Calibration \cite{Aubry14} & time \\
\hline\hline
HOG\cite{Dalal05}     & 72.3 / 65.0           &  31ms  & 60.4 / 50.2                 & 8.7 sec \\ 
WHO\cite{Hariharan12} & 82.1 / 85.4           &  3811ms& 84.4 / 83.0                 & 12.4 sec  \\
WHO-CG                & 81.7 / \textbf{84.9}  &  104ms & 83.7 / 87.3                 & 8.3 sec \\
WHO-CG-Z              & 54.4 / 65.1           &  103ms & \textbf{92.8} / 86.7        & 8.7 sec  \\
% NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
NZ-WHO-CG             & \textbf{90.0} / 82.8  &   79ms & 90.3 / \textbf{86.8}        & 8.5 sec   \\
\hline
\end{tabular}
\end{center}
\caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11} variations of WHO on 3DObject Car dataset\cite{Savarese07}. WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO. WHO-CG-Z uses whiten the whole template and zero out textureless region. NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method. The time column indicates the time to generate one template. We followed calibration procedure presented in \cite{Aubry14}.}
\label{tab:who_initializations}
\end{table*}
